\titleformat{\chapter}[display]
{\normalfont\Huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}

\titlespacing*{\chapter}{0pt}{50pt}{40pt}
\phantomsection
\chapter*{Reference}\\*[5cm]

%contant

\addcontentsline{toc}{chapter}{Reference}

Internet Resource
\begin{enumerate}
  \item Austin, E. (n.d.). Volvariella volvacea: The paddy straw mushroom identification & info. Healing Mushrooms. Retrieved October 20, 2024, from \href{https://healing-mushrooms.net/volvariella-volvacea}{https://healing-mushrooms.net/volvariella-volvacea}
  \item Selemin, J. (2023, September 28). The complete guide to paddy straw mushrooms. Shroomer. Retrieved October 20, 2024, from \href{https://www.shroomer.com/paddy-straw-mushroom/}{https://www.shroomer.com/paddy-straw-mushroom/}
  \item {\T คณะมนุษยศาสตร์และสังคมศาสตร์ มหาวิทยาลัยราชภัฏสุรินทร์ }admin{\T อนันต์.} (2016). {\T วิธีการเพาะเห็ดฟางในตะกร้าพลาสติก}. Available at: <\href{https://human.srru.ac.th/2016/08/15/วิธีการเพาะเห็ดฟางในตะ/}{https://human.srru.ac.th/2016/08/15/{\T วิธีการเพาะเห็ดฟางในตะกร้าพลาสติก}/}>
  \item (2008). {\fontsize{16}{24}\selectfont 草 菇 栽 培}. from \href{https://web.archive.org/web/20080506175441/http://www.tari.gov.tw/霧峰總所/植病系/研究室/食用菌類/草菇栽培.htm}{http://www.tari.gov.tw/{\fontsize{16}{24}\selectfont 霧峰總所}/{\fontsize{16}{24}\selectfont 植病系}/{\fontsize{16}{24}\selectfont 研究室}/{\fontsize{16}{24}\selectfont 食用菌類}/{\fontsize{16}{24}\selectfont 草菇栽培}.htm}
  \item Mushroom Mountain. (2020). How to Grow Paddy Straw Mushrooms (Volvariella volvacea). Available at: <\href{https://mushroommountain.com/how-to-grow-paddy-straw-mushrooms-volvariella-volvacea}{https://mushroommountain.com/how-to-grow-paddy-straw-mushrooms-volvariella-volvacea}/>
  \item calforlife. (2015). {\T พลังงานและสารอาหารจากเห็ด}, ฟาง. Available at: <\href{https://www.calforlife.com/th/calories/mushrooms-straw-canned-drained-solids}{https://www.calforlife.com/th/calories/mushrooms-straw-canned-drained-solids}>
  \item {\T กรมส่งเสริมการเกษตร}. (2023). Straw mushroom. Available at: <\href{https://www.doae.go.th/en/straw-mushroom/}{https://www.doae.go.th/en/straw-mushroom/}>
  \item Syndigo company. (2024). Straw Mushrooms. Available at: <\href{https://www.nutritionix.com/food/straw-mushrooms}{https://www.nutritionix.com/food/straw-mushrooms}>
  \item Specialty produce. n.d. Straw Mushrooms. Available at: <\href{https://specialtyproduce.com/produce/Straw_Mushrooms_18494.php}{https://specialtyproduce.com/produce/Straw\_Mushrooms\_18494.php}>
  \item Phyto biotech. n.d. Volvariella volvacea (Paddy straw mushroom). Available at: <\href{https://www.phytobiotech.in/volvariella-volvacea.html}{https://www.phytobiotech.in/volvariella-volvacea.html}>
  \item Dr. Nick Becker. (2024). Straw Mushrooms: The Easy Guide to Identify, Use, Cook, and Grow in 2024. Available at: <\href{https://climatesort.com/straw-mushrooms/}{https://climatesort.com/straw-mushrooms/}>
  \item {\T รักบ้านเกิดทีม}. (2009). {\T เห็ดฟาง}(straw mushroom). Available at: <\href{https://www.rakbankerd.com/agriculture/print.php?id=1328&s=tblplant}{https://www.rakbankerd.com/agriculture/print.php?id=1328&s=tblplant}>
  \item Disthai. n.d. {\T เห็ดฟาง ประโยชน์ดีๆ สรรพคุณเด่นๆและข้อมูลงานวิจัย}. Available at: <\href{https://www.disthai.com/17165926/เห็ดฟาง}{https://www.disthai.com/17165926/{\T เห็ดฟาง}}>
  \item Vinmec international hospital. n.d. What is the effect of mushroom?. Available at: <\href{https://www.vinmec.com/eng/article/what-is-the-effect-of-mushroom-en}{https://www.vinmec.com/eng/article/what-is-the-effect-of-mushroom-en}>
  \item {\T ศูนย์วิทยาศาสตร์เพื่อการศึกษา}. (2021). {\T กินเห็ดแล้วมีประโยชน์อย่างไร}. from \href{https://sciplanet.org/content/8846}{https://sciplanet.org/content/8846}
  \item {\T อำพล สุขเกตุ}. n.d. {\T โรคและปัญหาที่สำคัญในการเพาะเห็ดฟาง}. Available at: <\href{https://bassbio.com/index.php?option=com_content&view=article&id=69:2010-10-13-14-57-00}{https://bassbio.com/index.php?option=com\_content&view=article&id=69:2010-10-13-14-57-00}>
  \item {\fontsize{16}{24}\selectfont 邹长钱}. n.d. Method for processing dried straw mush-room. Available at: <\href{https://patents.google.com/patent/CN1200249A/en}{https://patents.google.com/patent/CN1200249A/en}>
  \item cookpad. n.d. {\T สูตร ผัดเห็ดฟาง} (53) {\T สูตร}. Available at: <\href{https://cookpad.com/th/search/ผัดเห็ดฟาง}{https://cookpad.com/th/search/{\T ผัดเห็ดฟาง}}>
  \item Just Agriculture. (2020). Mushroom cultivation: Pros and cons. Just Agriculture. Retrieved October 20, 2024, from \href{https://justagriculture.in/files/newsletter/nov/025%20Economic%20importance%20of%20mushroom%20and%20their%20Uses.pdf}{https://justagriculture.in/files/newsletter/nov/025\%20Econ omic\%20importance\%20of\%20mushroom\%20and\%20their\%20Uses.pdf}
\end{enumerate}
Book Resource
\begin{enumerate}
  \item National research center for mushroom. (2007). Cultivation technology of Paddy straw mushroom. Available at: <\href{https://dmrsolan.icar.gov.in/Bull_PSM.pdf}{https://dmrsolan.icar.gov.in/Bull\_PSM.pdf}>
  \item {\T กลุ่มสื่อส่งเสริมการเกษตรสำนักพัฒนาการถ่ายทอดเทคโนโลยีการส่งเสริมการเกษตร}. (2547) . {\T การเพาะเห็ดฟาง. สืบค้น} 20 {\T ตุลาคม} 2567. {\T จาก} \href{http://www.servicelink.doae.go.th/webpage/book%20PDF/mushroom/m009.pdf}{http://www.servicelink.doae.go.th/webpage/book\%20PDF/mushroom/m009.pdf}
  \item {\T อภิชาติ ศรีสอาด}.  (2023). {\T การเพาะปลูกเห็ดฟางคนเมือง} \& {\T เพื่อการค้า} 5 {\T ภาค}. {\T นาคา อินเตอร์มีเดีย}. {\T สืบค้น} 20 {\T ตุลาม} 2567.
  \item {\T ดร.จำลอง เพ็งคล้าย}. (2550). {\T เห็ดในประเทศไทย. กรุงเทพฯ: ราชบัณฑิตยสถาน. จาก} \href{https://opac.tistr.or.th/storage/LIBRARY/Books/2022/202266466.pdf}{https://opac.tistr.or.th/storage/LIBRARY/Books/2022/202266466.pdf}
  \item {\T วิทยา ทวีนุช}. (2565). {\T การเพาะเห็ดแบบเศรษฐกิจพอเพียง. สกายบุ๊คส์. สืบค้น} 20 {\T ตุลาคม} 2567. จาก \href{https://www.2ebook.com/new/library/book_detail/ldd/02008993}{https://www.2ebook.com/new/library/book\_detail/ldd/02008993}
  \item Paul Stamets J.S. Chilton. (1983). Mushroom Cultivator A Practical Guide to Growing Mushrooms at Home. Available at: \href{https://library.uniteddiversity.coop/Permaculture/Mushroom_Cultivator-A_Practical_Guide_to_Growing_Mushrooms_at_Home.pdf}{https://library.uniteddiversity.coop/Permaculture/Mushro om\_Cultivator-A\_Practical\_Guide\_to\_Growing\_Mushrooms\_at\_Home.pdf}
\end{enumerate}
Journal Resource
\begin{enumerate}
  \item USUBHARATANA, P.- PHUNGRASSAMI, H. (2015, 20 Dec). LIFE CYCLE ASSESSMENT OF THE STRAW MUSHROOM PRODUCTION. Retrieved October 20, 2024, from \href{https://www.aloki.hu/pdf/1401_189200.pdf}{\\ https://www.aloki.hu/pdf/1401\_189200.pdf}
  \item Sharifuddin, A. S., Ahmad, L. W., Mohamed, A., Sidek, N. J., Yunus, N. M., Yusof, S. C., Osman, N. D., & Rusli, I. S. (2023). Growth performance and fruiting body characterisation of the paddy straw mushroom (Volvariella volvacea) cultivated on different types of solid wastes . Asia-Pacific Journal of Science and Technology, 28(06), APST–28. \href{https://doi.org/10.14456/apst.2023.89}{https://doi.org/10.14456/apst.2023.89}
  \item {\T ขนิษฐา พรเจริญโรจน์}. (2563). {\T การปรับปรุงพันธุ์ เห็ดฟาง ไซโมแกรม การผสมพันธุ์  ใน รองศาสตราจารย์ ดร.ณัฐา โพธาภรณ์ (บ.ก.), ปีที่} 16 {\T ฉบับที่} 2 (2000): {\T วารสารเกษตร. ม.ป.ท.: ม.ป.พ.}
  \item Soravit Jamjumroon, Chalermchai Wongs-Aree, William B. McGlasson, Varit Srilaong, Piya Chalermklin, Sirichai Kanlayanarat, (2012, March). Extending the shelf-life of straw mushroom with high carbon dioxide treatment. Journal of Food Agriculture and Environment 10(1):78-84
  \item Preechaya Rungwikrikarn, (2024, 21 Feb). Guidelines for Promoting Low-Stack Straw Mushroom Cultivation with Cassava Pulp: A case study of Ban Suk Samran Straw Mushroom Group Community Enterprise Tha Kasem Sub-District Mueang Sa Kaeo District Sa Kaeo Province. Journal of Social Science for Local Development Rajabhat Maha Sarakham University 8(1)
  \item Zaidan, R. (2021). Sustainability perspectives for mushroom production: A case study for mushrooms in Malaysia. Frontiers in Sustainable Food Systems. Retrieved October 20, 2024, from \href{https://doi.org/10.3389/fsals.2021.736368}{https://doi.org/10.3389/fsals.2021.736368}
\end{enumerate}
